BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-12-31 Paper2/BOAST.tex
Added BEAST reference.

>>>>

BEAST~\cite{CPE:CPE3516} is an autotuning framework that uses macro-processing
in source files. Inside the macros, BEAST offers a DSL that can be used to
specify values derived from a set of iterators. Those iterators explore the
search space and can be constrained. Great care has been used to ensure that
the iterators enumeration as well as the pruning are as efficient as possible.
